Bioconductor workflow for single-cell RNA sequencing: Normalization, dimensionality reduction, clustering, and lineage inference

### 2017-07-07 workflow/workflow.Rmd
operating system comment and smaller K when more genes

[FP: todo before to convert to latex:

- try running workflow with more genes (DR if time),
- colors and labels in plotBarplot to compare original and our clustering (EP, DR),
- check removal cluster c4 (all)
- make singlecellworkflow package public (FP).]

[FP: todo after converting to latex (FP): 
- submit.]

@@

```{r parallel, echo=FALSE}
NCORES <- 2
mysystem = Sys.info()[["sysname"]]
if (mysystem == "Darwin"){
  registerDoParallel(NCORES)
  register(DoparParam())
}else if (mysystem == "Linux"){
  register(bpstart(MulticoreParam(workers=NCORES)))
}else{
  print("Please change this to allow parallel computing")
  register(SerialParam())
}
```

@@

Note that in the following, we assume that the user has access to a data folder located at `../data`. Users with a different directory stracture may need to change the `data_dir` variable below to reproduce the workflow.

```{r}
data_dir <- "../data/"

@@

As with most dimensionality reduction methods, the user needs to specify the number of dimensions for the new low-dimensional space. Here, we use `K = 50` dimensions and adjust for batch effects via the matrix `X`.

>>>>

@@

## Parallel computating

To give an idea to the users of the time needed to run the workflow, function `system.time` was used to report computation times for the time consuming functions. Computations were performed with 2 cores on a MacBook Pro (early 2015) with a 2.7 GHz Intel Core i5 processor and 8 GB of RAM. The `BiocParallel` package is used to allow for parallel computing in `zinbwave` function. Users with a different operating system may change the package used for parallel computing and the `NCORES` variable below.

```{r parallel}
NCORES <- 2
mysystem = Sys.info()[["sysname"]]
if (mysystem == "Darwin"){
  registerDoParallel(NCORES)
  register(DoparParam())
}else if (mysystem == "Linux"){
  register(bpstart(MulticoreParam(workers=NCORES)))
}else{
  print("Please change this to allow parallel computing on your computer.")
  register(SerialParam())
}
```

@@

Note that in the following, we assume that the user has access to a data folder located at `../data`. Users with a different directory structure may need to change the `data_dir` variable below to reproduce the workflow.

```{r datain}
data_dir <- "../data/"

@@

As with most dimensionality reduction methods, the user needs to specify the number of dimensions for the new low-dimensional space. Here, we use `K = 50` dimensions and adjust for batch effects via the matrix `X`. Note that if the users include more genes in the analysis, it may be preferable to reduce `K` to achieve a similar computational time.
